### 2017-09-08 paper/related.tex
pass on related work

\textit{Continuous integration services:}
Recent work showed us that Continuous Integration Services are widely
used and improve the productivity~\Fix{ref ref ref}.

>>>>

\textit{Continuous integration services:}
Recent work showed us that Continuous Integration Services are widely
used and improve the productivity~\cite{hilton-etal-ase2016}.
